Borel regularity for ODEs and Thimble Integrals

### 2023-11-01 exp-resurgence.tex
Updates from Overleaf

Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $\alpha_1,...,\alpha_N$ \footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form

@@

regarded as holomorphic functions in the position domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$. In fact, we introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ so that the function $I(z)$ will represent the Poincar\'e pairing.

@@

\begin{equation}
    H_{n}(B_j, B_j^+(\theta))\cong H_{n-1}(f^{-1}(p_j))\cong \begin{cases} \Z^{\mu_j} & \text{if } n=N\\
     0 & \text{otherwise}
    \end{cases}
\end{equation}
where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$ and $\mu_j$ is the Milnor number of the critical point $\alpha_j$.

@@

From the classical theory of singularities \cite{Arnold} we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value. 
Moreover, the vanishing cycles can be identified with the so-called \textit{Lefschetz thimbles}: since we assumed critical points to be non--degenerate, in a neighborhood of $\alpha_j$ there are local coordinates $x_1,...,x_N$ such that 
\[f=\alpha_j+\sum_{k=1}^N x_k^2\]

@@

Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_\alpha$, namely the integrals over Lefschetz thimbles labeled by the critical points $x_j\in\text{Crit}(f)$.

As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,k$ (and $l\neq j$). The jumps can be described geometrically using the theory of Picard--Lefschetz. Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies. We will discuss this phenomena from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions. \textcolor{orange}{[Can we comment more about this? For instance as a consequence of Theorem 3.3]}

@@

For each critical point $x_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j:=f(x_j)$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $x_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.

@@

on the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$. In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}. 
On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series. Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$. At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same. In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.

@@

As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}). Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain. We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}). Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the spatial domain.

Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface. If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$. If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).

@@

We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), the anharmonic oscillator...). Then, on the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in the proof of Theorem \ref{thm:maxim} part \ref{part3}. In the Airy example (\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function. Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.

@@

\subsection{thimble projection reasoning for the Airy function}\label{contour-argument}
Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$. Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
\begin{equation}\label{integral:mod-bessel-zeta}
K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
\end{equation}
For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below. Let's assume $z \in (0, \infty)$ for the rest of the section. \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
\begin{center}
\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
{\small The contour $\gamma_1$ in the $\zeta$ plane.}
\end{center}

@@

\section{Plan of the paper}
\subsection{Results}

\color{orange}
\begin{itemize}
\item what does it mean to be Borel regular?
\item when does it happen?
\begin{itemize}
\item State new Borel regularity results
\begin{itemize}
\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
\begin{itemize}
\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
\item Also contextualize with Loday-Richaud
\end{itemize}
\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
\begin{equation}
\begin{tikzcd}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
& \\
\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
\end{tikzcd}
\end{equation}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item thimble projection formula
\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
\end{itemize}
%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
\end{itemize}
\end{itemize}

\color{orange}
\subsection*{Outline}

\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}

\begin{enumerate}
\item introduction
\begin{itemize}
\item Exponential integrals
\begin{itemize}
\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
\item the choice of the path $\mathcal{C}$: 
\begin{itemize}
\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
\end{itemize}
\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
\begin{itemize}
\item there is a comparison isomorphism (Maxim)
\end{itemize}
\item varying $z$ we have the Stokes phenomena
\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
\begin{itemize}
\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
\item it is an example of resurgent series (\'Ecalle)
\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$. There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism   
\end{itemize} 
\end{itemize}
\item what are exponential integrals? \textcolor{gray}{has to be done}
\begin{itemize}
\item motivation
\begin{itemize}
\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
\item In physics ??
\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
\end{itemize}
\end{itemize}
\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
\item State results about resurgence of exponential integrals and Stokes phenomena
\begin{itemize}
\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
\item ODE and fractional derivative formula [{\tt draft2}]
\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
\end{itemize}
\end{itemize}
\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
\begin{enumerate}
\item Analytic
\begin{enumerate}
\item Introduction
\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
\item The Laplace transform of a holomorphic function
\begin{enumerate}
\item Over an ordinary point
\item Over a branch point
\item Differential equation
\end{enumerate}
\item Relating differential equations in the frequency domain to integral equations in the position domain
\end{enumerate}
\item Formal
\begin{enumerate}
\item Laplace transform of a formal series
\item Borel transform
\item Relating differential equations in the frequency variable to integral equations in the position variable
\end{enumerate}
\end{enumerate}
\item Review of integral equations
\begin{itemize}
\item Existence of solutions
\item Fractional integrals and derivatives
\item Going between integral and differential equations (slight functions)
\end{itemize}
\item General cases
\begin{enumerate}
\item Borel regularity
\begin{itemize}
\item General ODE of the form
\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
\begin{itemize}
\color{DarkCyan}
\item More generally, for $P$ of degree $n$, we should be able to handle
\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
\begin{itemize}
\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
\end{itemize}
\color{orange}
\item Show that we can find a slight solution at each critical value.
\item Show that $\hat{\iota} = \tilde{\iota}$, where:
\begin{itemize}
\item $I = \laplace \iota$
\item $\hat{\iota}$ is the Taylor expansion of $\iota$
\item $\tilde{I}$ is the asymptotic series of $I$
\item $\tilde{\iota} = \borel \tilde{I}$
\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
\end{itemize}
\end{itemize}
\item General thimble integral (conditions?)
\begin{itemize}
\item Proof of Borel regularity
\item $3/2$-derivative formula
\item thimble projection reasoning
\end{itemize}
\end{itemize}
\item Resurgence
\begin{itemize}
\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
\item Relate to \'Ecalle's formalism and the alien derivative
\item Stokes factors
\begin{itemize}
\item For ODEs
\item For thimble integrals
\end{itemize}
\end{itemize}
\end{enumerate}
\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
\begin{enumerate}
\item The Airy example
\begin{itemize}
\item $I(z)$ is a solution of a linear ODE. We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
\item Compute Stokes constants
\begin{itemize}
\item Using thimble projection formula and Borel transform computation [{\tt draft2}]
\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
\end{itemize}
\item Comparison with the literature \textcolor{gray}{has to be done}
\begin{itemize}
\item Mari\~{n}o
\item Sauzin
\item Kontsevich slides
\item Kawai--Takei? [might take too long to understand well enough]
\end{itemize}
\end{itemize}
\item The Airy--Lucas examples
\begin{itemize}
\item Compute Borel transform [{\tt airy-resurgence}]
\item Compute Stokes constants \textcolor{gray}{has to be done}
\end{itemize}
\item Bessel 0 (it is different because we have infinite cover)
\begin{itemize}
\item Compute Stokes constants [{\tt draft2}]
\end{itemize}
\item Bessel $\mu$ (follows from Bessel 0)
\begin{itemize}
\item Compute Stokes constants [{\tt modified Bessel}]
\end{itemize}
\item The generalized Airy example
\item The vibrating beam example
\begin{itemize}
\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals since Andy is interested in that sort of thing
\end{itemize}
\end{enumerate}
\end{enumerate}

\subsection{Why Borel regularity works for thimble integrals}
\color{DarkBlue}
\begin{itemize}
%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
%\begin{itemize}
%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
%\end{itemize} 
\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial. His proof uses microlocal analysis and classical results due to Varchenko. In the same algebraic setting, Malgrange states the Borel regularity result \cite[Theorem 6]{Malgrange22} 
\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
%\begin{equation}
%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
%\end{equation}

%then the following diagram is commutative
%\begin{equation}
%\begin{tikzcd}
%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
%& \\
%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
%\end{tikzcd}
%\end{equation}
\begin{itemize}
%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item A corollary of [Thm 4] is the thimble projection formula.
\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
\begin{equation}
mmm
\end{equation} 
\end{itemize}
\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim). See also the argument of KS21 sec 6.2 in the framework of analytic WCFs. 
\begin{itemize}
\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
\end{itemize}
\end{itemize}
\color{black}

>>>>

Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form

@@

regarded as holomorphic functions in the frequency domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$. In fact, we introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ so that the function $I(z)$ will represent the Poincar\'e pairing.

@@

\begin{equation}
    H_{n}(B_j, B_j^+(\theta))\cong H_{n-1}(f^{-1}(p_j))\cong \begin{cases} \Z^{\mu_j} & \text{if } n=N\\
     0 & \text{otherwise}
    \end{cases}
\end{equation}
where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$ and $\mu_j$ is the Milnor number of the critical \textcolor{red}{point/value $a_j/\alpha_j$}.

@@

From the classical theory of singularities \cite{Arnold} we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value. 
Moreover, the vanishing cycles can be identified with the so-called \textit{Lefschetz thimbles}: since we assumed critical points to be non--degenerate, in a neighborhood of $a_j$ there are local coordinates $x_1,...,x_N$ such that 
\[f=\alpha_j+\sum_{k=1}^N x_k^2\]

@@

Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_j$, namely the integrals over Lefschetz thimbles labeled by the critical points $a_j\in\text{Crit}(f)$.

As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,N$ (and $l\neq j$). The jumps can be described geometrically using the theory of Picard--Lefschetz. Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies. We will discuss this phenomena from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions. \textcolor{orange}{[Can we comment more about this? For instance as a consequence of Theorem 3.3]}

@@

For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.

@@

on the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$. In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}. 
On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series. Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$. \textcolor{red}{At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.--I think we realise they have the same expansion at $\alpha_j$, thus they must agree.} In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.

@@

As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}). Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain. We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}). Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the \textcolor{red}{spatial/frequency?} domain.

Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface. If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$. If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).

@@

We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, \textcolor{red}{we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.} On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in the proof of Theorem \ref{thm:maxim} part \ref{part3}. In the Airy example (see Section \ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and \textcolor{red}{by numerical check we show $\hat{\phi}_j$ is a simple resurgent function. Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.}

@@

\subsection{Thimble projection reasoning for the Airy function}\label{contour-argument}
Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$. Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
\begin{equation}\label{integral:mod-bessel-zeta}
K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
\end{equation}
For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below. Let's assume $z \in (0, \infty)$ for the rest of the section. \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
\begin{center}
\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
{\small The contour $\gamma_1$ in the $\zeta$ plane.}
\end{center}

@@
